Light inextensible strings under tension in the Schwarzschild geometry

### 2019-08-28 string_physics_teacher.tex
more work

\noindent which would give~$R$ as a function of~$\left(r,r'\right)$.
Considering~$r'(\phi)=0$ shows that if a string is tangential at a
point with~$r_0>2M$, then it has a radius of curvature of~$r_0^2/2M$
at that point.  Any circular path, including a circular orbit
at~$r=r_0$, has a radius of curvature of $r_0<r_0^2/2M$, showing that
circular orbits cannot follow a taut string at closest approach (as in
the classical case).  Also observe that null geodesics have a radius
of curvature of $r_0^2/3M < r_0^2/2M$, showing that light cannot
follow a taut string at closest approach either: tangential string
looks curved to a local observer.

>>>>

\noindent which would give~$R$ as a function of~$\left(r,r'\right)$.
Considering~$r'(\phi)=0$ shows that if a string is tangential at a
point with~$r_0>2M$, then it has a radius of curvature of~$r_0^2/2M$
there.  Tangential null geodesics have a radius of curvature of
$r_0^2/3M$, strictly less than that of a string.  This shows that a
taut string would {\em look} curved to a local observer, having a
(visual) radius of curvature of $r_0^2/6M$.  At the photon sphere of a
solar mass black hole, such a string would appear to have a radius of
about $2\unit{km}$, a readily understandable result.
